---
title: "ARC- HDSR (Marti & Smith, 2022)"
author: "Deniz Marti and Michael Smith"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document: 
      code_folding: hide
      
---

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
# Load libraries and settings

knitr::opts_chunk$set(
    warning = FALSE,
    message = FALSE,
    comment = "#>",
    fig.path = "figs/", # Plot save path
    fig.width = 7.252, # Plot dimensions
    fig.height = 4,
    fig.retina = 3 # Better plot resolution
)
```


Setup libraries
```{r setup libraries, message=FALSE, warning=FALSE}

#Load libraries and settings

library(knitr)
library(lubridate)
library(tidyverse)
library(here)
library(readxl)
library(psych)
library(GPArotation)
library(nFactors)
library(reshape)
library(lubridate)
library (fcuk)
library(ggplot2)
library(janitor)
#install.packages("corrr")
library(MASS)
install.packages("openxlsx")
library(openxlsx)
#install.packages("lme4") 
#install.packages("Matrix")

library(lme4)
library(corrr)

options(
    htmltools.dir.version = FALSE,
    knitr.table.format = "html",
    knitr.kable.NA = '',
    tibble.width = Inf)
knitr::opts_chunk$set(
    warning = FALSE,
    message = FALSE,
    fig.retina = 3)
dplyr.width = Inf


```

##  Read in DSR data

```{r raw data}

dataDSR <- read_xlsx(here::here("data","HDSR_data.xlsx"),sheet = "Auth_Rich_1" ) 

## clean the names
dataDSR=dataDSR%>%janitor::clean_names()
head(dataDSR)

```

## T tests for authenticity and upvotes 
(measurements related to the comments)
We used independent sample Student t test to compare the measurements of two years. 

```{r t test}
#t.test for authenticity score
dataDSR%>%t.test(authentic ~ year, data = .)
#ANOVA for authenticity score, controlling for the effect of different documents
dataDSR%>%aov(authentic ~ year+document, data = .)%>%summary()

#t.test for upvotes per comment
dataDSR%>%t.test(upvotes ~ year, data = .)
#ANOVA for upvotes score, controlling for the effect of different documents
dataDSR%>%aov(upvotes ~ year+document, data = .)%>%summary()


#describe for auth. mean and SD-- summary statistics
dataDSR%>%dplyr::filter(year=="2020")%>% describe()
dataDSR%>%dplyr::filter(year=="2021")%>% describe()

```

## Preprocessing for discussion summaries
 
```{r quality DSR}

dataDSR_2 <- read_xlsx(here::here("data","HDSR_data.xlsx"),sheet = "Auth_Rich_2" ) # 
#clean names
dataDSR_2=dataDSR_2%>%janitor::clean_names()
## quality 
dataDSR_2=dataDSR_2%>%dplyr::select(-"submission")

#filter 2020 data
dataDSR_2_2020=dataDSR_2%>%filter(year=="2020")
#filter 2021 data
dataDSR_2_2021=dataDSR_2%>%filter(year=="2021")


#summary of 2020 data
df.summary_2020 <- dataDSR_2_2020 %>%    
  group_by(conversation_no) %>%
  summarise(qualityscore = round(sum(quality),2), #quality score of a discussion grouped by "conversation_no"
            comment_count_indiscussion=n(), # number of comments in a discussion
            mean_replies=round(mean(replies),2), #avg replies in a discussion
            mean_upvotes=round(mean(upvotes),2) #avg upvotes in a discussion
  )%>%mutate(year="2020") # include a year variable
df.summary_2020=df.summary_2020%>%mutate(discussion_ornot=case_when(comment_count_indiscussion>1~1, TRUE~0)) # when there is one comment in a conversation, variable score is set to zero. 



#summary of 2021 data 
df.summary_2021 <- dataDSR_2_2021 %>%    
  group_by(conversation_no) %>%
  summarise(qualityscore = round(sum(quality),2),
            comment_count_indiscussion=n(),
            mean_replies=round(mean(replies),2),
            mean_upvotes=round(mean(upvotes),2)
  )%>%mutate(year="2021")
df.summary_2021=df.summary_2021%>%mutate(discussion_ornot=case_when(comment_count_indiscussion>1~1, TRUE~0))


```

## T tests for the quality scores and avg. replies
(measurements related to the discussions)
```{r t test quality}

t.test(df.summary_2020$discussion_ornot,df.summary_2021$discussion_ornot)

df.summary_2020%>%describe()

df.summary_2021%>%describe()

t.test(df.summary_2020$mean_replies,df.summary_2021$mean_replies)

```



# T-tests

## Mean Replies 
```{r for discussion}

#identify the discussions, comment_count>1
df.summary_2020_filtered=df.summary_2020%>%dplyr::filter(comment_count_indiscussion>1)
df.summary_2021_filtered=df.summary_2021%>%dplyr::filter(comment_count_indiscussion>1)
# t.test for discussion
t.test(df.summary_2020_filtered$qualityscore,df.summary_2021_filtered$qualityscore)

t.test(df.summary_2020_filtered$mean_replies,df.summary_2021_filtered$mean_replies)

#describe for SD
df.summary_2020_filtered%>%describe()
df.summary_2021_filtered%>%describe()


```

## For Binary Discussion 
```{r quality binary}
qualdata=rbind(df.summary_2020,df.summary_2021) # combine 2020 and 2021 data summaries

qualdata=qualdata%>%filter(comment_count_indiscussion>1)%>%
  mutate(quality_ornot=case_when(qualityscore==0 ~0,
                                                  TRUE ~1))
# operationalize quality as binary variable (set to zero if the original score is zero and set to 1 otherwise)

# t test for the binary quality score
qualdata%>%t.test(quality_ornot ~ year, data = .)

qualdata%>%dplyr::filter(year=="2020")%>%describe()
qualdata%>%dplyr::filter(year=="2021")%>%describe()

```


## For authenticity binary scoring
```{r authentic binary}

# authenti_ornot is a binary variable which takes zero value if the score is originally zero, 1 otherwise.
MikeDSR=MikeDSR%>%mutate(authenti_ornot=case_when(authentic==0 ~0,
                                                  TRUE ~1))
#t test to compare binary authenticity scores of the years
MikeDSR%>%t.test(authenti_ornot ~ year, data = .)

#summary statistics
MikeDSR%>%dplyr::filter(year=="2020")%>%describe()
MikeDSR%>%dplyr::filter(year=="2021")%>%describe()

```


## Ggplots

### Plot Auth. Scores
```{r auth score ggplot}

df.summary <- MikeDSR %>%
  group_by(year) %>%
  summarise(
    sd = sd(authentic, na.rm = TRUE)/sqrt(length(authentic)), #we take sqrt because we look at the averages
    mean = mean(authentic)
  )
df.summary
#relabeling
df.summary$year<-factor (df.summary$year, levels = c(
 "2020",
 "2021"),
 labels=c("Spring 2020\nSemester","Spring 2021\nSemester"))

p1<-ggplot(df.summary, aes(x=as.factor(year), y=mean)) +
  geom_col(aes(fill = year), position = position_dodge(0.8), width = 0.2)+
  geom_errorbar(
    aes(ymin = mean-2*sd, ymax = mean+2*sd),
    position =position_dodge(0.2), width = 0.1
    )+
  geom_point(aes(color = year), position = position_dodge(0.2))+
  labs(title="Authentic Comments per Semester",
       y="Average Authenticity Score") +
  ylim(0,1)+
 theme(legend.position = "none",
       axis.title.x = element_blank())

p1

ggsave(here::here("figures","MikeDSR_authenticity.jpg"))

```

## Data Prep for Auth. Binary Score
```{r auth binary score}
df.summary <- MikeDSR %>%
  group_by(year) %>%
  summarise(
    sd = sd(authenti_ornot, na.rm = TRUE)/sqrt(length(authenti_ornot)), #we take sqrt because we look at the averages
    mean = mean(authenti_ornot)
  )

df.summary
#relabeling
df.summary$year<-factor (df.summary$year, levels = c(
 "2020",
 "2021"),
 labels=c("Spring 2020","Spring 2021"))

# add a variable that indicates the authenticity scores
df.summary$metric = c("Authenticity Scores\nin Comments")

```

## Plot Data Prep for Quality Score

```{r prep for qual}

df.summary_qual <- qualdata %>%
  group_by(year) %>%
  summarise(
    sd = sd(quality_ornot, na.rm = TRUE)/sqrt(length(quality_ornot)), #we take sqrt because we look at the averages
    mean = mean(quality_ornot)
  )


df.summary_qual
#relabeling
df.summary_qual$year<-factor (df.summary_qual$year, levels = c(
 "2020",
 "2021"),
 labels=c("Spring 2020","Spring 2021"))


df.summary_qual$metric = c("Quality Scores\nin Discussions")
```

## Data Prep for Tabular form
Combine authenticity and quality for tabular form
```{r prep}

df.summary_tabular = rbind(df.summary, df.summary_qual)

```
## Tabular Ggplots
```{r tabular form facet wrap}

p_tab<-ggplot(df.summary_tabular, aes(x=as.factor(year), y=mean)) +
  geom_col(aes(fill = year), position = position_dodge(0.8), width = 0.2)+
  geom_errorbar(
    aes(ymin = mean-1.96*sd, ymax = mean+1.96*sd), # 1.96 for 95% CI
    position =position_dodge(0.2), width = 0.1
    )+ facet_grid(. ~ metric)+
  geom_point(position = position_dodge(0.2))+
  labs(title="Authenticity of Comments and Quality of \nDiscussions per Semester",
       y="Percentages of Metrics") + theme_minimal(base_size = 18) + 
 theme(legend.position = "none",text = element_text(size=18,colour="black"),
       axis.title.x = element_blank())+scale_y_continuous(labels = scales::percent)+expand_limits(y = c(0, 1))  + scale_fill_grey() 

ggsave(here::here("figures","HDSR_tabular.jpg"))


```
